On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] Mention higher dimensions
[AMZr] Code cosmetics
[AMZr] A brief remark on the characteristic of a cen-circ PIPS

The computation of exact values of $d(m,n)$ is a difficult problem.
In 2003, Solymosi proved~\cite{solymosi2003note} that $d(2,n) \geq cn$ for some constant $c$;
now it is known~\cite{my-pps-linear-bound-2019} that $c>5/11$.
So, even finding the estimates is not easy.

@@

@@

\begin{equation}\label{formula2}
d(m, (k - \alpha)m + \alpha) \leq \operatorname{diam(\mathcal{P})},
\end{equation}

>>>>

The computation of exact values of $d(m,n)$ is a difficult problem.
In 2003, Solymosi proved~\cite{solymosi2003note} that $d(2,n) \geq cn$ for some constant $c$;
now it is known~\cite{my-pps-linear-bound-2019} that $c>5/11$.
The most recent advances for higher dimensions can be found in~\cite{nozaki2013lower}.
So, even finding the estimates is not easy.

@@

\begin{remark}
	Every centered-circular point set has characteristic 1.
	Indeed, let $\mathcal{P} = \{M_0, M_1,$ $ M_2, M_3, ..., M_k\}$ be a centered-circular point set
	with $M_0$ being the center.
	According to the sine formula, in the triangle $M_1 M_2 M_3$
	\begin{equation}
		\sin \angle M_1 M_2 M_3 = \frac{|M_1M_3|}{2R}
		,
	\end{equation}
	where $R = |M_0 M_1| $ is the radius of the triangle's circumcircle.
	Then the area of the triangle $M_1 M_2 M_3$ is
	\begin{equation}
		S = \frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \sin \angle M_1 M_2 M_3 =
		\frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \frac{|M_1M_3|}{2|M_0 M_1|} \in\mathbb Q
		.
	\end{equation}
\end{remark}

@@

\begin{equation}\label{formula2}
d(m, (k - \alpha)m + \alpha) \leq \operatorname{diam}(\mathcal{P}),
\end{equation}
